---
title: "Treatment x Crkt time"
author: "Kaitlyn Campbell"
date: "1/14/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
Imidacloprid Experiment Summer 2019

# Load packages and data
```{r}
library(brms)
library(dplyr)
library(ggplot2)
library(tibble)  
library(tidyverse)
library(readr)
library(faintr)
library(devtools)
library(rstan)
library(rstantools)
library(readr)
library(tidybayes)
library(bayesplot)

lab <- read_csv("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Brain_IMI_Data.csv")

#View(lab)
lab$Treatment <- as.factor(lab$Treatment)
```

# Wrangle that data, cowboy
```{r}
# Rename Crkt time columns with date
lab <- lab %>% 
  rename(July_4_19 = CRKT_sec_July_4) %>% 
  rename(July_8_19 = CRKT_sec_July_8) %>% 
  rename(July_11_19 = CRKT_sec_July_11)

# Take 'date' row names and make them into 1 column & fill with crkt time
lab_long <- lab %>% 
  gather(key = "Crkt_date", value = "Crkt_time", -Animal_ID, -Treatment, -Mass_g_June_26, -Mass_g_July_3, -Mass_g_July_10, -Mass_g_July_17, -TL_mm_June_26, -TL_mm_July_17, -IMI_ng_g_tissue, -IMI_ole_ng_g_tissue, -IMI_ng_mg_protein, -IMI_ole_ng_mg_protein)

# Make Crkt_date a factor
lab_long$Crkt_date <- as.factor(lab_long$Crkt_date)
lab_long$Treatment <- as.factor(lab_long$Treatment)

# Determine mean crkt times by treatment and date
lab_long %>% 
  group_by(Treatment, Crkt_date) %>% 
  summarize(mean= mean(Crkt_time)) 

# Visualize crkt time by date and treatment
level_order <- c('July_4_19', 'July_8_19', 'July_11_19') 

lab_long %>% 
  ggplot(aes(x=factor(Crkt_date, level=level_order), y=Crkt_time)) +
  geom_boxplot(aes(fill = Treatment), position = position_dodge(1)) +
  scale_y_log10() +
  labs(x="Date")

# Visualize overall crkt time by treatment
lab_long %>% 
  ggplot(aes(x=Treatment, y=Crkt_time)) +
  geom_boxplot(aes(fill = Treatment), position = position_dodge(1)) +
  geom_jitter(aes(fill=Treatment), color="black", shape=21, width=0.25) +
  scale_y_log10() + facet_wrap(~Crkt_date)

lab_long %>% 
  group_by(Treatment) %>% 
  summarize(mean_crkt_time = mean(Crkt_time),
         median_crkt_time = median(Crkt_time))
```

# Visualize mean crkt time
```{r}
hist(lab_long$Crkt_time)
```
Max time = 120 seconds (we stopped timing the frogs after 2 minutes so we weren't stuck there all day)

# Load fit_crkt14 model
```{r}
# load saved model
load("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/saved_models/fit_crkt14.rda")

fit_crkt14 <- brm(Crkt_time ~ Treatment + Crkt_date + (1|Animal_ID), data = lab_long, family = Gamma(link = "log"),
    prior=c(prior(normal(3, 1), class=Intercept),
            prior(normal(0, 1.5), class = b),
            prior(exponential(8), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE))

conditional_effects(fit_crkt14)
print(fit_crkt14, prior=T)
plot(fit_crkt14)
```

# Extract posteriors
```{r}
set.seed(4545)
post_crkt14 <- posterior_samples(fit_crkt14)  # puts chains of model into data frame
head(post_crkt14)
nrow(post_crkt14) # 6000
```

# Compute averages for each treatment category
```{r}
as_tibble(post_crkt14) %>% 
  mutate(iteration = 1:nrow(post_crkt14))

# 0 trt on July_11
fit_0_J11 <- data.frame(value = exp(post_crkt14$b_Intercept), type = "0", date = "July_11_19", iter = 1:nrow(post_crkt14)) 

# 0 trt on July_4
fit_0_J4 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Crkt_dateJuly_4_19), type = "0", date = "July_4_19", iter = 1:nrow(post_crkt14)) 

# 0 trt on July_8
fit_0_J8 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Crkt_dateJuly_8_19), type = "0", date = "July_8_19", iter = 1:nrow(post_crkt14)) 

mu_0 <- rbind(fit_0_J11, fit_0_J4, fit_0_J8)

# 0.1 trt on July_11
fit_0.1_J11 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment0.1), type = "0.1", date = "July_11_19", iter = 1:nrow(post_crkt14)) 

# 0.1 trt on July_4
fit_0.1_J4 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment0.1 + post_crkt14$b_Crkt_dateJuly_4_19), type = "0.1", date = "July_4_19", iter = 1:nrow(post_crkt14)) 

# 0.1 trt on July_8
fit_0.1_J8 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment0.1 + post_crkt14$b_Crkt_dateJuly_8_19), type = "0.1", date = "July_8_19", iter = 1:nrow(post_crkt14)) 

mu_0.1 <- rbind(fit_0.1_J11, fit_0.1_J4, fit_0.1_J8)

# 1 trt on July_11
fit_1_J11 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment1), type = "1", date = "July_11_19", iter = 1:nrow(post_crkt14)) 

# 1 trt on July_4
fit_1_J4 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment1 + post_crkt14$b_Crkt_dateJuly_4_19), type = "1", date = "July_4_19", iter = 1:nrow(post_crkt14)) 

# 1 trt on July_8
fit_1_J8 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment1 + post_crkt14$b_Crkt_dateJuly_8_19), type = "1", date = "July_8_19", iter = 1:nrow(post_crkt14)) 

mu_1 <- rbind(fit_1_J11, fit_1_J4, fit_1_J8)

# 5 trt on July_11
fit_5_J11 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment5), type = "5", date = "July_11_19", iter = 1:nrow(post_crkt14)) 

# 5 trt on July_4
fit_5_J4 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment5 + post_crkt14$b_Crkt_dateJuly_4_19), type = "5", date = "July_4_19", iter = 1:nrow(post_crkt14)) 

# 5 trt on July_8
fit_5_J8 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment5 + post_crkt14$b_Crkt_dateJuly_8_19), type = "5", date = "July_8_19", iter = 1:nrow(post_crkt14)) 

mu_5 <- rbind(fit_5_J11, fit_5_J4, fit_5_J8)

# 10 trt on July_11
fit_10_J11 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment10), type = "10", date = "July_11_19", iter = 1:nrow(post_crkt14)) 

# 10 trt on July_4
fit_10_J4 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment10 + post_crkt14$b_Crkt_dateJuly_4_19), type = "10", date = "July_4_19", iter = 1:nrow(post_crkt14)) 

# 10 trt on July_8
fit_10_J8 <- data.frame(value = exp(post_crkt14$b_Intercept + post_crkt14$b_Treatment10 + post_crkt14$b_Crkt_dateJuly_8_19), type = "10", date = "July_8_19", iter = 1:nrow(post_crkt14)) 

mu_10 <- rbind(fit_10_J11, fit_10_J4, fit_10_J8)

mu_fit <- rbind(mu_0, mu_0.1, mu_1, mu_5, mu_10)
View(mu_fit)
```

# Summary stats from posterior with 95% CI
```{r}
crkt2_summary <- mu_fit %>% 
  group_by(date) %>% 
  summarize(mean = mean(value),
            median= median(value),
            sd = sd(value),
            low89 = quantile(value, probs = 0.055),
            high89 = quantile(value, probs = 0.945)) %>%
  mutate_if(is.numeric,round,2)

crkt2_summary
```
   type  date        mean median    sd low89 high89
 1 0     July_11_19 11.0   10.4   3.64  6.32  17.4 
 2 0     July_4_19  14.5   13.7   5.29  7.82  24.0 
 3 0     July_8_19   5.78   5.44  2.13  3.12   9.51
 4 0.1   July_11_19 22.3   21.0   8.14 12.0   37.2 
 5 0.1   July_4_19  29.2   27.6  10.4  15.8   47.8 
 6 0.1   July_8_19  11.6   10.9   4.07  6.43  18.8 
 7 1     July_11_19 34.8   32.7  12.8  18.8   57.1 
 8 1     July_4_19  45.6   42.8  16.7  24.7   75.6 
 9 1     July_8_19  18.1   17.1   6.38  9.9   29.4 
10 5     July_11_19 25.9   24.2   9.91 13.4   43.8 
11 5     July_4_19  33.8   31.8  12.4  17.9   55.6 
12 5     July_8_19  13.4   12.5   4.67  7.43  21.7 
13 10    July_11_19 16.1   15.3   5.93  8.6   26.6 
14 10    July_4_19  21.2   19.9   7.81 11.1   35.0 
15 10    July_8_19   8.46   7.87  3.21  4.45  14.1

  type   mean median    sd low89 high89
1 0      10.4   9.53  5.3   3.88   19.8
2 0.1    21.0  19.2  10.8   7.89   40.4
3 1      32.9  30.0  17.0  12.3    63.5
4 5      24.3  22.0  12.7   9.06   47.4
5 10     15.2  14.0   7.92  5.56   29.4

  date        mean median    sd low89 high89
1 July_11_19  22.0   19.4 11.9   8.18   43.7
2 July_4_19   28.8   25.8 15.5  10.5    57.0
3 July_8_19   11.5   10.3  6.05  4.22   22.3

```{r}
lab_long %>% 
  group_by(Treatment) %>% 
  summarize(mean = mean(Crkt_time),
            median = median(Crkt_time))
```


# make plot with facet by feeding trial date
# legend displays colors for treatment groups
```{r}
# make new facet labels
# make a column in 'summary_4' called 'facet'
crkt2_summary$facet = factor(crkt2_summary$date, levels = c("July_4_19", "July_8_19", "July_11_19"))

# rename the levels in the 'facet' column
levels(crkt2_summary$facet) <- c("July 4", "July 8", "July 11")

# values provide color blind palette
crkt_date_trt <- crkt2_summary %>% 
  ggplot(aes(x=type, y=mean, ymin=low89, ymax=high89, fill=type)) + 
  geom_point(size=4, position=position_dodge(width=0.4), shape=21)+
  geom_errorbar(width=0.1, position=position_dodge(width=0.4)) +
  xlab("Treatment (µg/L)")+
  ylab("Response Time (sec)")+
  theme_classic()+
  scale_fill_manual(name="Treatment (µg/L)",  values = c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b"))+
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10"))+
  facet_grid(. ~ facet)
crkt_date_trt

crkt_date_trt <- crkt_date_trt + scale_x_discrete(labels= conclabels)
crkt_date_trt

#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/crkt_date_trt.tiff", crkt_date_trt, dpi=400, width=5, height=3, units="in")
```

```{r}
mu_fit$facet = factor(mu_fit$date, levels = c("July_4_19", "July_8_19", "July_11_19"))

# rename the levels in the 'facet' column
levels(mu_fit$facet) <- c("July 4", "July 8", "July 11")

# Rename by name: change "July_4_19" to "July 4"
levels(lab_long$Crkt_date)[levels(lab_long$Crkt_date)=="July_4_19"] <- "July 4"
levels(lab_long$Crkt_date)[levels(lab_long$Crkt_date)=="July_8_19"] <- "July 8"
levels(lab_long$Crkt_date)[levels(lab_long$Crkt_date)=="July_11_19"] <- "July 11"

levels(mu_fit$facet) <- c("July 4", "July 8", "July 11")
#levels(lab_long$facet) <- c("July 4", "July 8", "July 11")

ggplot()+
  geom_boxplot(data=mu_fit, aes(x=type, y=value), outlier.shape = NA) +
  geom_jitter(data=lab_long, aes(x=Treatment, y=Crkt_time, color=Treatment), width=0.4, size=0.5) +
  xlab("Treatment (µg/L)")+
  ylab("Response Time (sec)")+
  #scale_y_log10() +
  theme_classic()+ 
  scale_fill_manual(name="Treatment (µg/L)",  values = c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b"))+
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10")) + facet_grid(.~facet) + ylim(c(0,120))

ggplot(data=lab_long, aes(x=Treatment, y=Crkt_time, color=Treatment)) + geom_boxplot(outlier.shape = NA) + geom_jitter(size=0.5) + scale_y_log10()
```

# PLOT
```{r}
# reponse time faceted by trial date
response_time_plot <- ggplot()+
  geom_violin(data=mu_fit, aes(x=type, y=value, fill=type) , position = "dodge") +
  geom_boxplot(data=mu_fit, aes(x=type, y=value, fill=type), outlier.shape = NA, width = 0.2, position = position_dodge(0.9)) +
  geom_jitter(data=lab_long, aes(x=Treatment, y=Crkt_time), width=0.25, shape=1, size=0.5) +
  labs(x = "Treatment (µg/L)", 
       y = "Response Time (sec)",
       fill= "Treatment (µg/L)") +
  theme_classic()+ 
  scale_fill_manual(name="Treatment (µg/L)",  values = c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b"))+
  theme(plot.caption = element_text(hjust = 0)) +
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10")) + 
  #ylim(c(0,120)) + 
  scale_y_log10() +
  facet_wrap(~facet , ncol=1)
response_time_plot

# average response times from all trial dates
mean_response_time_plot <- ggplot()+
  geom_violin(data=mu_fit, aes(x=type, y=value, fill=type) , position = "dodge") +
  geom_boxplot(data=mu_fit, aes(x=type, y=value, fill=type), outlier.shape = NA, width = 0.2, position = position_dodge(0.9)) +
  geom_jitter(data=lab_long, aes(x=Treatment, y=Crkt_time), width=0.25, shape=1, size=0.5) +
  labs(x = "Treatment (µg/L)", 
       y = "Response Time (sec)",
       fill= "Treatment (µg/L)") +
  theme_classic()+ 
  scale_fill_manual(name="Treatment (µg/L)",  values = c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b"))+
  theme(plot.caption = element_text(hjust = 0)) +
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10")) + 
  #ylim(c(0,120)) + 
  scale_y_log10() 
mean_response_time_plot

#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/mean_response_time_plot.tiff", mean_response_time_plot, dpi=400, width=5, height=3, units="in")
```

# Probability that differences between trt groups are greater than 0
```{r}
## key:
# fit_0_J4 = trt 0 on July 4
# fit_0.1_J4 = trt 0.1 on July 4
# fit_1_J4 = trt 1 on July 4
# fit_5_J4 = trt 5 on July 4

# trt 0 vs 0.1 on july 4
diff_Crkt0_0.1_J4 <- fit_0.1_J4$value - fit_0_J4$value
mean(diff_Crkt0_0.1_J4) # 14.66917
quantile(diff_Crkt0_0.1_J4,probs=c(0.055,0.945)) # (0.5272638, 31.9497325)
sum(diff_Crkt0_0.1_J4>0)/6000 # 95.2%

# trt 0 vs 1 on july 4
diff_Crkt0_1_J4 <- fit_1_J4$value - fit_0_J4$value
mean(diff_Crkt0_1_J4) # 31.12534
quantile(diff_Crkt0_1_J4,probs=c(0.055,0.945)) # (10.25992, 60.34138)
sum(diff_Crkt0_1_J4>0)/6000 # 99.53%

# trt 0 vs 5 on july 4
diff_Crkt0_5_J4 <- fit_5_J4$value - fit_0_J4$value
mean(diff_Crkt0_5_J4) # 19.23987
quantile(diff_Crkt0_5_J4,probs=c(0.055,0.945)) # ( 3.243473 , 39.940813 )
sum(diff_Crkt0_5_J4>0)/6000 # 97.5%

# trt 0 vs 10 on july 4
diff_Crkt0_10_J4 <- fit_10_J4$value - fit_0_J4$value
mean(diff_Crkt0_10_J4) # 6.660439
quantile(diff_Crkt0_10_J4,probs=c(0.055,0.945)) # (-5.141245 20.490826)
sum(diff_Crkt0_10_J4>0)/6000 # 81.52%%

# trt 0 vs 0.1 on july 8
diff_Crkt0_0.1_J8 <- fit_0.1_J8$value - fit_0_J8$value
mean(diff_Crkt0_0.1_J8) # 5.813551
quantile(diff_Crkt0_0.1_J8,probs=c(0.055,0.945)) # (0.22570 12.66137)
sum(diff_Crkt0_0.1_J8>0)/6000 # 95.2%

# trt 0 vs 1 on july 8
diff_Crkt0_1_J8 <- fit_1_J8$value - fit_0_J8$value
mean(diff_Crkt0_1_J8) # 12.32459
quantile(diff_Crkt0_1_J8,probs=c(0.055,0.945)) # (4.160636 , 23.205177)
sum(diff_Crkt0_1_J8>0)/6000 # 99.53%

# trt 0 vs 5 on july 8
diff_Crkt0_5_J8 <- fit_5_J8$value - fit_0_J8$value
mean(diff_Crkt0_5_J8) # 7.56783
quantile(diff_Crkt0_5_J8,probs=c(0.055,0.945)) # ( 1.366031 , 15.557908)
sum(diff_Crkt0_5_J8>0)/6000 # 97.47%

# trt 0 vs 10 on july 8
diff_Crkt0_10_J8 <- fit_10_J8$value - fit_0_J8$value
mean(diff_Crkt0_10_J8) # 2.676283
quantile(diff_Crkt0_10_J8,probs=c(0.055,0.945)) # (-2.120903  , 8.220580)
sum(diff_Crkt0_10_J8>0)/6000 # 81.52% 

# trt 0 vs 0.1 on july 11
diff_Crkt0_0.1_J11 <- fit_0.1_J11$value - fit_0_J11$value
mean(diff_Crkt0_0.1_J11) # 11.3677
quantile(diff_Crkt0_0.1_J11,probs=c(0.055,0.945)) # ()
sum(diff_Crkt0_0.1_J11>0)/6000 # 95.18%

# trt 0 vs 1 on july 11
diff_Crkt0_1_J11 <- fit_1_J11$value - fit_0_J11$value
mean(diff_Crkt0_1_J11) # 23.87567
quantile(diff_Crkt0_1_J11,probs=c(0.055,0.945)) # ()
sum(diff_Crkt0_1_J11>0)/6000 # 99.53%

# trt 0 vs 5 on july 11
diff_Crkt0_5_J11 <- fit_5_J11$value - fit_0_J11$value
mean(diff_Crkt0_5_J11) # 14.90513
quantile(diff_Crkt0_5_J11,probs=c(0.055,0.945)) # ()
sum(diff_Crkt0_5_J11>0)/6000 # 97.46%

# trt 0 vs 10 on july 11
diff_Crkt0_10_J11 <- fit_10_J11$value - fit_0_J11$value
mean(diff_Crkt0_10_J11) # 5.173828
quantile(diff_Crkt0_10_J11,probs=c(0.055,0.945)) # ()
sum(diff_Crkt0_10_J11>0)/6000 # 81.52%
```

# Compare differences over all 3 feeding trial dates dates
```{r}
# trt 0 vs 0.1 overall (all dates)
diff_Crkt0_0.1 <- mu_0.1$value - mu_0$value
mean(diff_Crkt0_0.1) # 10.61681
quantile(diff_Crkt0_0.1,probs=c(0.055,0.945)) # (0.3526513 26.5642224)
sum(diff_Crkt0_0.1>0)/18000 # 95.18% ; this is divided by 18,000 b/c there are now 18,000 observations in mu_0.1 and mu_0 instead of only 6,000 (like in post_fit_crkt2)

# trt 0 vs 1 overall (all dates)
diff_Crkt0_1 <- mu_1$value - mu_0$value
mean(diff_Crkt0_1) # 22.44187
sd(diff_Crkt0_1) # 14.60733
quantile(diff_Crkt0_1,probs=c(0.055,0.945)) # (5.780215 , 48.774999)
sum(diff_Crkt0_1>0)/18000 # 99.53%

# trt 0 vs 5 overall (all dates)
diff_Crkt0_5 <- mu_5$value - mu_0$value
mean(diff_Crkt0_5) # 13.90428
quantile(diff_Crkt0_5,probs=c(0.055,0.945)) # (1.942204 , 33.115224)
sum(diff_Crkt0_5>0)/18000 # 97.47%

# trt 0 vs 10 overall (all dates)
diff_Crkt0_10 <- mu_10$value - mu_0$value
mean(diff_Crkt0_10) # 4.83685
sd(diff_Crkt0_10) # 6.503312
quantile(diff_Crkt0_10,probs=c(0.055,0.945)) # (-3.503181 , 16.183335)
sum(diff_Crkt0_10>0)/18000 # 81.52%
```
```{r}
# trt 0.1 vs 1 overall (all dates)
diff_Crkt1_0.1 <- mu_1$value - mu_0.1$value
mean(diff_Crkt1_0.1) # 11.82506
quantile(diff_Crkt1_0.1,probs=c(0.055,0.945)) # (-5.292284 36.208887)
sum(diff_Crkt1_0.1>0)/18000 # 85.88%

# trt 0.1 vs 5 overall (all dates)
diff_Crkt5_0.1 <- mu_5$value - mu_0.1$value
mean(diff_Crkt5_0.1) # 3.287469
quantile(diff_Crkt5_0.1,probs=c(0.055,0.945)) # (-12.30712 21.17529)
sum(diff_Crkt5_0.1>0)/18000 # 63.53%

# trt 0.1 vs 10 overall (all dates)
diff_Crkt10_0.1 <- mu_0.1$value - mu_10$value
mean(diff_Crkt10_0.1) # 5.779957
quantile(diff_Crkt10_0.1,probs=c(0.055,0.945)) # (-6.407244 21.064419)
sum(diff_Crkt10_0.1>0)/18000 # 78.25%

# trt 1 vs 10 overall (all dates)
diff_Crkt10_1 <- mu_1$value - mu_10$value
mean(diff_Crkt10_1) # 17.60502
quantile(diff_Crkt10_1,probs=c(0.055,0.945)) # (1.510035 , 43.106377)
sum(diff_Crkt10_1>0)/18000 # 96.67%

# trt 1 vs 5 overall (all dates)
diff_Crkt5_1 <- mu_1$value - mu_5$value
mean(diff_Crkt5_1) # 8.537591
quantile(diff_Crkt5_1,probs=c(0.055,0.945)) # (-10.10629 , 32.40667)
sum(diff_Crkt5_1>0)/18000 # 76.73%

# trt 1 vs 5 overall (all dates)
diff_Crkt5_10 <- mu_5$value - mu_10$value
mean(diff_Crkt5_10) # 9.067426
quantile(diff_Crkt5_10,probs=c(0.055,0.945)) # (-4.124177 , 27.685015)
sum(diff_Crkt5_10>0)/18000 # 85.83%
```

# Where feeding response times among trts different across trial dates?
```{r 0 trt}
# trt 0 on July 4 vs 0 on july 8 or july 11
diff_Crkt0_J4_J8 <- fit_0_J4$value - fit_0_J8$value # july 4 vs july 8th
mean(diff_Crkt0_J4_J8) # 8.722635
quantile(diff_Crkt0_J4_J8,probs=c(0.055,0.945)) # (2.698985, 19.037227)
sum(diff_Crkt0_J4_J8>0)/6000 # 99.88%

diff_Crkt0_J4_J11 <- fit_0_J4$value - fit_0_J11$value # July 4 vs July 11
mean(diff_Crkt0_J4_J11) # 3.541354
quantile(diff_Crkt0_J4_J11,probs=c(0.055,0.945)) # (-3.618526, 12.725914)
sum(diff_Crkt0_J4_J11>0)/6000 # 83.32%

diff_Crkt0_J11_J8 <- fit_0_J11$value - fit_0_J8$value # July 11 vs July 8
mean(diff_Crkt0_J11_J8) # 5.181281
quantile(diff_Crkt0_J11_J8,probs=c(0.055,0.945)) # (0.6956264, 11.9119869)
sum(diff_Crkt0_J11_J8>0)/6000 # 98.83%
```
```{r 0.1 trt}
# trt 0.1 on July 4 vs 0 on july 8 or july 11
diff_Crkt0.1_J4_J8 <- fit_0.1_J4$value - fit_0.1_J8$value # july 4 vs july 8th
mean(diff_Crkt0.1_J4_J8) # 17.57825
quantile(diff_Crkt0.1_J4_J8,probs=c(0.055,0.945)) # (5.246264, 38.449623)
sum(diff_Crkt0.1_J4_J8>0)/6000 # 0.9988333

diff_Crkt0.1_J4_J11 <- fit_0.1_J4$value - fit_0.1_J11$value # July 4 vs July 11
mean(diff_Crkt0.1_J4_J11) # 6.842823
quantile(diff_Crkt0.1_J4_J11,probs=c(0.055,0.945)) # (-7.716029, 23.790050)
sum(diff_Crkt0.1_J4_J11>0)/6000 # 0.8331667

diff_Crkt0.1_J11_J8 <- fit_0.1_J11$value - fit_0.1_J8$value # July 11 vs July 8
mean(diff_Crkt0.1_J11_J8) # 10.73543
quantile(diff_Crkt0.1_J11_J8,probs=c(0.055,0.945)) # (1.232895, 26.638464)
sum(diff_Crkt0.1_J11_J8>0)/6000 # 0.9883333
```
```{r 1 trt}
# trt 1 on July 4 vs 0 on july 8 or july 11
diff_Crkt1_J4_J8 <- fit_1_J4$value - fit_1_J8$value # july 4 vs july 8th
mean(diff_Crkt1_J4_J8) # 27.52338
quantile(diff_Crkt1_J4_J8,probs=c(0.055,0.945)) # (8.086888, 60.938009)
sum(diff_Crkt1_J4_J8>0)/6000 # 0.9988333

diff_Crkt1_J4_J11 <- fit_1_J4$value - fit_1_J11$value # July 4 vs July 11
mean(diff_Crkt1_J4_J11) # 10.79102
quantile(diff_Crkt1_J4_J11,probs=c(0.055,0.945)) # (-12.28315, 38.74079)
sum(diff_Crkt1_J4_J11>0)/6000 # 0.8331667

diff_Crkt1_J11_J8 <- fit_1_J11$value - fit_1_J8$value # July 11 vs July 8
mean(diff_Crkt1_J11_J8) # 16.73236
quantile(diff_Crkt1_J11_J8,probs=c(0.055,0.945)) # (1.811796, 41.265540)
sum(diff_Crkt1_J11_J8>0)/6000 # 0.9883333
```
```{r 5 trt}
# trt 5 on July 4 vs 0 on july 8 or july 11
diff_Crkt5_J4_J8 <- fit_5_J4$value - fit_5_J8$value # july 4 vs july 8th
mean(diff_Crkt5_J4_J8) # 20.39467
quantile(diff_Crkt5_J4_J8,probs=c(0.055,0.945)) # (5.885447, 45.043352)
sum(diff_Crkt5_J4_J8>0)/6000 # 0.9988333

diff_Crkt5_J4_J11 <- fit_5_J4$value - fit_5_J11$value # July 4 vs July 11
mean(diff_Crkt5_J4_J11) # 7.876093
quantile(diff_Crkt5_J4_J11,probs=c(0.055,0.945)) # (-9.086507, 28.049928)
sum(diff_Crkt5_J4_J11>0)/6000 # 0.8331667

diff_Crkt5_J11_J8 <- fit_5_J11$value - fit_5_J8$value # July 11 vs July 8
mean(diff_Crkt5_J11_J8) # 12.51858
quantile(diff_Crkt5_J11_J8,probs=c(0.055,0.945)) # (1.380559, 31.702011)
sum(diff_Crkt5_J11_J8>0)/6000 # 0.9883333
```
```{r 10 trt}
# trt 5 on July 4 vs 0 on july 8 or july 11
diff_Crkt10_J4_J8 <- fit_10_J4$value - fit_10_J8$value # july 4 vs july 8th
mean(diff_Crkt10_J4_J8) # 12.70679
quantile(diff_Crkt10_J4_J8,probs=c(0.055,0.945)) # (3.764372, 27.441084)
sum(diff_Crkt10_J4_J8>0)/6000 # 0.9988333

diff_Crkt10_J4_J11 <- fit_10_J4$value - fit_10_J11$value # July 4 vs July 11
mean(diff_Crkt10_J4_J11) # 5.027965
quantile(diff_Crkt10_J4_J11,probs=c(0.055,0.945)) # (-5.681152, 18.738569)
sum(diff_Crkt10_J4_J11>0)/6000 # 0.8331667

diff_Crkt10_J11_J8 <- fit_10_J11$value - fit_10_J8$value # July 11 vs July 8
mean(diff_Crkt10_J11_J8) # 7.678825
quantile(diff_Crkt10_J11_J8,probs=c(0.055,0.945)) # (0.8708955, 18.7445897)
sum(diff_Crkt10_J11_J8>0)/6000 # 0.9883333
```

```{r}
mu_july4_all_trt <- mu_fit %>% 
  filter(date == "July_4_19")

mu_july8_all_trt <- mu_fit %>% 
  filter(date == "July_8_19")

mu_july11_all_trt <- mu_fit %>% 
  filter(date == "July_11_19")

diff <- mu_july4_all_trt$value - mu_july8_all_trt$value
mean(diff) # 17.38515
sd(diff) # 11.1219
quantile(diff,probs=c(0.055,0.945)) # (3.81548, 45.96478)
sum(diff>0)/30000 # 0.9988333

diff <- mu_july4_all_trt$value - mu_july11_all_trt$value
mean(diff) # 6.815851
quantile(diff,probs=c(0.055,0.945)) # (-7.781502, 28.278934)
sum(diff>0)/30000 # 0.8331667

diff <- mu_july11_all_trt$value - mu_july8_all_trt$value
mean(diff) # 10.5693
sd(diff) # 7.818099
quantile(diff,probs=c(0.055,0.945)) # (0.9780268, 30.8286892)
sum(diff>0)/30000 # 0.9883333
```
