---
title: "Untitled"
author: "Kaitlyn Campbell"
date: "1/8/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
Imidacloprid Experiment Summer 2019

# Load packages and data
```{r}
library(brms)
library(dplyr)
library(ggplot2)
library(tibble)  
library(tidyverse)
library(readr)
library(faintr)
library(devtools)
library(rstan)
library(rstantools)
library(readr)
library(tidybayes)
library(bayesplot)

lab <- read_csv("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Brain_IMI_Data.csv")

lab$Treatment <- as.factor(lab$Treatment)

# Rename Mass_g_date columns with just the date
lab <- lab %>% 
  rename(June_26 = Mass_g_June_26) %>% 
  rename(July_3 = Mass_g_July_3) %>% 
  rename(July_10 = Mass_g_July_10) %>% 
  rename(July_17 = Mass_g_July_17)
```

# function from jeff that prevents you from having to manually extract averages from the posterior (this will also prevent you from making dumn calculation errors...hopefully)
```{r}
conditional_posts_fitted_no_effects <- function(fit){
list_of_data <- conditional_effects(fit)[[1]]
col_i <- which(colnames(list_of_data) == names(fit$data[1])) - 1
new_names <- list_of_data[(1:col_i)]

as_tibble(t(fitted(fit, newdata = list_of_data, re_formula = NA, summary = FALSE))) %>%
  cbind(new_names) %>%
  pivot_longer(cols = contains("V"), names_to = "iter") %>%
  mutate(iter = parse_number(iter))
} # this function should work fine now
```

# Load model
```{r}
load("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/saved_models/fit23.7.rda")

fit23.7 <- brm(IMI_ng_mg_protein ~ Treatment, data = lab, family = Gamma(link = "log"), 
              prior=c(prior(normal(2, 1), class=Intercept),
                  prior(normal(1, 2.5), class = b, coef ="Treatment0.1"),
                  prior(normal(2, 2.5), class = b, coef ="Treatment1"),
                  prior(normal(2, 2.5), class = b, coef ="Treatment5"),
                  prior(normal(4, 2.5), class = b, coef ="Treatment10"),
                  prior(exponential(1), class = shape)),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE))

#save(fit23.7, file = "/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/saved_models/fit23.7.rda")

conditional_effects(fit23.7)

print(fit23.7)
pp_check(fit23.7, type = "boxplot", notch=FALSE)
pp_check(fit23.7, type="hist")
pp_check(fit23.7, nsamples=100)
pp_check(fit23.7, type='stat', stat='mean')
plot(fit23.7)
```

# Extract posteriors from fit9
```{r}
set.seed(4545)
post_fit <- posterior_samples(fit23.7)    # puts chains of model into data frame
head(post_fit)
nrow(post_fit) # 6000
```

# Compute averages for each treatment category
```{r}
as_tibble(post_fit) %>% 
  mutate(iteration = 1:nrow(post_fit))

fit_0 <- data.frame(value = exp(post_fit$b_Intercept), type = "0", iter = 1:nrow(post_fit))

fit_0.1 <- data.frame(value = exp(post_fit$b_Intercept + post_fit$b_Treatment0.1), type = "0.1", iter = 1:nrow(post_fit))

fit_1 <- data.frame(value = exp(post_fit$b_Intercept + post_fit$b_Treatment1), type = "1", iter = 1:nrow(post_fit))

fit_5 <- data.frame(value = exp(post_fit$b_Intercept + post_fit$b_Treatment5), type = "5", iter = 1:nrow(post_fit))

fit_10 <- data.frame(value = exp(post_fit$b_Intercept + post_fit$b_Treatment10), type = "10", iter = 1:nrow(post_fit))

mu_fit <- rbind(fit_0, fit_0.1, fit_1, fit_5, fit_10)
View(mu_fit)
```

# Summary stats from posterior with 95%
```{r}
mu_fit_summary <- mu_fit %>% 
  group_by(type) %>% 
  summarize(mean = mean(value),
            median = median(value),
            sd = sd(value),
            low89 = quantile(value, probs = 0.055),
            high89 = quantile(value, probs = 0.945)) %>%
  mutate_if(is.numeric,round,2)

mu_fit_summary
```
 # from fit23.7 w/ 89% CrI:
  type     mean  median     sd   low89  high89
1 0        4.36    4.32   0.56    3.56    5.31
2 0.1     52.7    52.2    6.71   43.2    64.1 
3 1      114.    113.    14.5    93.4   139.  
4 5      582.    577.    74     473.    706.  
5 10    1365.   1351.   172.   1115.   1654.

# make figure for model summaries
```{r}
mu_fit_summary %>% 
  ggplot(aes(x=type, y=mean, ymin=low89, ymax=high89, fill=type)) + 
  geom_point(size=4, position=position_dodge(width=0.4), shape=21)+ scale_y_log10() +
  geom_errorbar(width=0.1, position=position_dodge(width=0.4)) +
  xlab("Treatment (µg/L)")+
  ylab("Imidacloprid \nBrain Concentration \n(ng/mg protein)")+
  labs(caption = "Summary of imidacloprid brain concentrations in \nNorthern Leopard frogs by treatment. Results are averages \nand 95% credible intervals from the posterior distribution of \na Bayesian generalized linear mixed model. Y-axis is on the \nlog scale.",
       fill= "Treatment (µg/L)")+
  theme_classic()+
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10"))+
  theme(plot.caption = element_text(hjust = 0))
```

```{r}
imi_trtp <- mu_fit_summary %>% 
  ggplot(aes(x=type, y=mean, ymin=low89, ymax=high89, fill=type)) + 
  geom_point(size=4, position=position_dodge(width=0.4), shape=21)+ scale_y_log10() +
  geom_errorbar(width=0.1, position=position_dodge(width=0.4)) +
  xlab("Treatment (µg/L)")+
  ylab("Imidacloprid \nBrain Concentration \n(ng/mg protein)")+
  labs(caption = "Summary of imidacloprid brain concentrations in Northern \nLeopard frogs by treatment. Results are averages and 95% \ncredible intervals from the posterior distribution of a Bayesian \ngeneralized linear mixed model. Y-axis is on the log scale.",
fill= "Treatment (µg/L)") +
  theme_classic() +
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10"))+
  theme(plot.caption = element_text(hjust = 0))
imi_trtp

#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/imi_trtp.tiff", imi_trtp, dpi=400, width=5, height=3, units="in")
```

# Visualize probability mass
```{r}
# add color blind palette 
#cbbPalette <- c("#999999", "#E69F00", "#009E73", "#D55E00", "#56B4E9")

# new color palette
colorpalette <- c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b")

imi_trt <- ggplot() +
  geom_violin(data=mu_fit, aes(x=type, y=value, fill=type), position = "dodge") +
  geom_boxplot(data=mu_fit, aes(x=type, y=value, fill=type), outlier.shape = NA, width = 0.1, position = position_dodge(0.9)) +
  geom_jitter(data=lab, aes(x=Treatment, y=IMI_ng_mg_protein), size=0.5, shape=1, width = 0.25) +
  labs(x = "Treatment (µg/L)", 
       y = "Imidacloprid\nBrain Concentration \n(ng/mg protein)",
       fill= "Treatment (µg/L)") +
  theme(text= element_text(size=20), 
        plot.title = element_text(face = "bold", hjust = 0.5),
        plot.caption=element_text(size=10)) +
  theme_classic() + scale_fill_manual(values=colorpalette) + 
  theme(plot.caption = element_text(hjust = 0)) +
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10"))+
  scale_y_log10()
imi_trt

#scale_fill_manual(values=colorpalette, labels=c("0", "0.5", "5", "25", "50"))

# save plot
#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/imi_trt.tiff", imi_trt, dpi=400, width=5, height=3, units="in")


# create labels with the correct concentrations on the x-axis
#conclabels <- c("0", "0.5", "5", "25", "50")
#imi_trt_p <- imi_trt + scale_x_discrete(labels= conclabels) # add labels
#imi_trt_p

# if you want to animate this figure:
library(gganimate)
library(av)
library(gifski)
library(png)
imi_trt_p + transition_states(type, wrap=FALSE) + shadow_mark() + enter_grow() + enter_fade()

# add caption back in for future figures
## caption = "Fig. # Comparison of imidacloprid brain concentrations \n(ng/mg protein) in Northern Leopard frogs by treatment. \nResults are averages and 95% credible intervals from the \nposterior distribution of a Bayesian generalized linear mixed \nmodel. Y axis is on the log scale."
```

# calculate average difference of IMI in brain btwn trts
```{r}
## 0 vs. 0.1 trt
fit_0_0.1 <- post_fit %>% 
  transmute(dif = exp(post_fit$b_Intercept + post_fit$b_Treatment0.1) - exp(post_fit$b_Intercept))

mean(fit_0_0.1$dif) 
## 48.37397 = avg difference between 0.1 and 0 trt

quantile(fit_0_0.1$dif,probs=c(0.055,0.945)) 
##     5.5%    94.5% 
## 38.72248 59.71442 

sum(fit_0_0.1$dif>0)/6000  
## There is more than a 0.99% probability that control frog body mass was different at the start vs end of experiment

fit_0_1 <- post_fit %>% 
  transmute(dif = exp(post_fit$b_Intercept + post_fit$b_Treatment1) - exp(post_fit$b_Intercept))
mean(fit_0_1$dif)  # 109.9912
quantile(fit_0_1$dif,probs=c(0.055,0.945))  # (88.98029 , 134.30007)
sum(fit_0_1$dif>0)/6000  

fit_0_5 <- post_fit %>% 
  transmute(dif = exp(post_fit$b_Intercept + post_fit$b_Treatment5) - exp(post_fit$b_Intercept))
mean(fit_0_5$dif)  # 577.3183
quantile(fit_0_5$dif,probs=c(0.055,0.945))  # (468.7432 , 701.6808)
sum(fit_0_5$dif>0)/6000 

fit_0_10 <- post_fit %>% 
  transmute(dif = exp(post_fit$b_Intercept + post_fit$b_Treatment10) - exp(post_fit$b_Intercept))
mean(fit_0_10$dif)  # 1360.748
quantile(fit_0_10$dif,probs=c(0.055,0.945))  # (1111.416 , 1649.624)
sum(fit_0_10$dif>0)/6000 
```

# Group differences w/ 95% CI
```{r}
group_diffs <- mu_fit_summary %>% 
  mutate(diff_means = mean - lead(mean))
group_diffs
```
  type     mean  median     sd   low89  high89 diff_means
1 0        4.36    4.32   0.56    3.56    5.31      -48.4
2 0.1     52.7    52.2    6.71   43.2    64.1       -61.6
3 1      114.    113.    14.5    93.4   139.       -467. 
4 5      582.    577.    74     473.    706.       -783. 
5 10    1365.   1351.   172.   1115.   1654.         NA