---
title: "Untitled"
author: "Kaitlyn Campbell"
date: "2/11/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
IMI Lab experiment
# Load packages and data
```{r}
library(brms)
library(dplyr)
library(ggplot2)
library(tibble)  
library(tidyverse)
library(readr)
library(faintr)
library(devtools)
library(rstan)
library(rstantools)
library(readr)
library(tidybayes)
library(bayesplot)
```
```{r}
lab <- read_csv("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Brain_IMI_Data.csv")

lab$Treatment <- as.factor(lab$Treatment)

# Rename Mass_g_date columns with just the date
lab <- lab %>% 
  rename(June_26 = Mass_g_June_26) %>% 
  rename(July_3 = Mass_g_July_3) %>% 
  rename(July_10 = Mass_g_July_10) %>% 
  rename(July_17 = Mass_g_July_17)

# Make a new column named 'Mass_date' and fill it with the dates that we just created above. Then make another new column named 'Mass_g' and fill the column with mass_g values that correspond to each date in the new 'Mass_date' column
lab_long <- lab %>% 
  gather(key = "Mass_date", value = "Mass_g", -Animal_ID, -Treatment, -TL_mm_June_26, -TL_mm_July_17, -IMI_ng_g_tissue, -IMI_ole_ng_g_tissue, -IMI_ng_mg_protein, -IMI_ole_ng_mg_protein, -CRKT_sec_July_4, -CRKT_sec_July_8, -CRKT_sec_July_11)

# Make Mass_date a factor
lab_long$Mass_date <- as.factor(lab_long$Mass_date)
lab_long$Treatment <- as.factor(lab_long$Treatment)
```

# Plot raw data
```{r}
lab_long %>% 
  ggplot(aes(x=Treatment, y= Mass_g)) + geom_violin() + geom_boxplot(width=.1) + facet_wrap(. ~ Mass_date)

lab_long %>% 
  ggplot(aes(x=Treatment, y= Mass_g)) + geom_violin() + geom_point(size=.5) + facet_wrap(. ~ Mass_date)

lab_long %>% 
  group_by(Mass_date, Treatment) %>% 
  summarize(mean_mass = mean(Mass_g))
```
  Mass_date Treatment mean_mass
June_26   0              20.6
June_26   0.1            18.8
June_26   1              17.3
June_26   5              21.0
June_26   10             15.5

July_3    0              20.4
July_3    0.1            18.6
July_3    1              16.6
July_3    5              19.9
July_3    10             14.4

July_10   0              21.4
July_10   0.1            19.0
July_10   1              17.0
July_10   5              20.3
July_10   10             15.2

July_17   0              18.4
July_17   0.1            16.9
July_17   1              15.1
July_17   5              18.6
July_17   10             13.4

# Gamma distribution
# Add Mass date into model
```{r}
load("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/saved_models/Models_used_in_paper/fit_11.rda")

fit_11 <- brm(Mass_g ~ Treatment * Mass_date + (1|Animal_ID), data = lab_long, family = Gamma(link = "log"), prior=c(prior(normal(3, 2), class=Intercept),
                  prior(normal(0, 1), class = b),
                  prior(exponential(0.01), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE))

print(fit_11)
pp_check(fit_11, type = "dens_overlay", resp = "Mass_g", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Intercept", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Treatment0.1", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Treatment1", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Treatment1", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Treatment5", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Treatment10", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Mass_date_July_10", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Mass_date_July_17", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Mass_date_June_26", nsamples=100)
pp_check(fit_11, type = "dens_overlay", resp = "Mass_date_July_3", nsamples=100)

lab_long %>%
  tidybayes::add_predicted_draws(model = fit_11, n = 100) %>%
  ungroup() %>%
  ggplot(aes(x = .prediction, group = .draw)) +
  geom_line(stat = 'density',
            alpha = 0.1,
            colour = 'blue') +
  geom_line(stat = 'density',
            data = lab_long,
            mapping = aes(x = Mass_g, group = NULL),
            colour = 'black',
            size = 1.5) +
  scale_y_continuous(NULL, breaks = NULL) +
  labs(x = expression(paste('Mass_g density ')),
       title = 'Mass_g density, actual versus predicted') +
  facet_wrap(~ Treatment)


loo_fit_11 <- loo(fit_11, save_psis = TRUE, cores = 2, moment_match = TRUE)
print(loo_fit_11) # ok = 32
plot(loo_fit_11, label_points = TRUE)

yrep <- posterior_predict(fit_11)
ppc_loo_pit_overlay(lab_long$Mass_g, 
                    yrep = yrep, 
                    lw = weights(loo_fit_11$psis_object))


# reorder levels in lab_long
lab_long$Mass_date <- factor(lab_long$Mass_date, levels = c("June_26", "July_3", "July_10", "July_17"))

print(fit_11)
pp_check(fit_11, type = "boxplot", notch=FALSE)
pp_check(fit_11, type="hist")
pp_check(fit_11, nsamples=100)
pp_check(fit_11, type='stat', stat='mean')
plot(fit_11)

plot(conditional_effects(fit_11), points = T)
```

```{r}
post_fit_11 <- posterior_samples(fit_11)
nrow(post_fit_11) # 6000
head(post_fit_11)

as_tibble(post_fit_11) %>% 
  mutate(iteration = 1:nrow(post_fit_11))

# 0 trt on June_26
fit_0_J26 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Mass_dateJune_26), type = "0", date = "June_26", iter = 1:nrow(post_fit_11)) 

# 0 trt on July_10
fit_0_J10 <- data.frame(value = exp(post_fit_11$b_Intercept), type = "0", date = "July_10", iter = 1:nrow(post_fit_11)) 

# 0 trt on July_3
fit_0_J3 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Mass_dateJuly_3), type = "0", date = "July_3", iter = 1:nrow(post_fit_11)) 

# 0 trt on July_17
fit_0_J17 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Mass_dateJuly_17), type = "0", date = "July_17", iter = 1:nrow(post_fit_11)) 

mu_0 <- rbind(fit_0_J26, fit_0_J10, fit_0_J3, fit_0_J17)

# 0.1 trt on June_26
fit_0.1_J26 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment0.1 + post_fit_11$b_Mass_dateJune_26 + post_fit_11$`b_Treatment0.1:Mass_dateJuly_17`), type = "0.1", date = "June_26", iter = 1:nrow(post_fit_11)) 

# 0.1 trt on July_10
fit_0.1_J10 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment0.1), type = "0.1", date = "July_10", iter = 1:nrow(post_fit_11)) 

# 0.1 trt on July_3
fit_0.1_J3 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment0.1 + post_fit_11$b_Mass_dateJuly_3 + post_fit_11$`b_Treatment0.1:Mass_dateJuly_3`), type = "0.1", date = "July_3", iter = 1:nrow(post_fit_11)) 

# 0.1 trt on July_17
fit_0.1_J17 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment0.1 + post_fit_11$b_Mass_dateJuly_17 + post_fit_11$`b_Treatment1:Mass_dateJuly_17`), type = "0.1", date = "July_17", iter = 1:nrow(post_fit_11)) 

mu_0.1 <- rbind(fit_0.1_J26, fit_0.1_J10, fit_0.1_J3, fit_0.1_J17)

# 1 trt on June_26
fit_1_J26 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment1 + post_fit_11$b_Mass_dateJune_26 + post_fit_11$`b_Treatment1:Mass_dateJune_26`), type = "1", date = "June_26", iter = 1:nrow(post_fit_11)) 

# 1 trt on July_10
fit_1_J10 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment1), type = "1", date = "July_10", iter = 1:nrow(post_fit_11)) 

# 1 trt on July_3
fit_1_J3 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment1 + post_fit_11$b_Mass_dateJuly_3 + post_fit_11$`b_Treatment1:Mass_dateJuly_3`), type = "1", date = "July_3", iter = 1:nrow(post_fit_11)) 

# 1 trt on July_17
fit_1_J17 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment1 + post_fit_11$b_Mass_dateJuly_17 + post_fit_11$`b_Treatment1:Mass_dateJuly_17`), type = "1", date = "July_17", iter = 1:nrow(post_fit_11)) 

mu_1 <- rbind(fit_1_J26, fit_1_J10, fit_1_J3, fit_1_J17)

# 5 trt on June_26
fit_5_J26 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment5 + post_fit_11$b_Mass_dateJune_26 + post_fit_11$`b_Treatment5:Mass_dateJune_26`), type = "5", date = "June_26", iter = 1:nrow(post_fit_11))

# 5 trt on July_10
fit_5_J10 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment5), type = "5", date = "July_10", iter = 1:nrow(post_fit_11)) 

# 5 trt on July_3
fit_5_J3 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment5 + post_fit_11$b_Mass_dateJuly_3 + post_fit_11$`b_Treatment5:Mass_dateJuly_3`), type = "5", date = "July_3", iter = 1:nrow(post_fit_11)) 

# 5 trt on July_17
fit_5_J17 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment5 + post_fit_11$b_Mass_dateJuly_17 + post_fit_11$`b_Treatment5:Mass_dateJuly_17`), type = "5", date = "July_17", iter = 1:nrow(post_fit_11)) 

mu_5 <- rbind(fit_5_J26, fit_5_J10, fit_5_J3, fit_5_J17)

# 10 trt on June_26
fit_10_J26 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment10 + post_fit_11$b_Mass_dateJune_26 + post_fit_11$`b_Treatment10:Mass_dateJune_26`), type = "10", date = "June_26", iter = 1:nrow(post_fit_11))

# 10 trt on July_10
fit_10_J10 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment10), type = "10", date = "July_10", iter = 1:nrow(post_fit_11)) 

# 10 trt on July_3
fit_10_J3 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment10 + post_fit_11$b_Mass_dateJuly_3 + post_fit_11$`b_Treatment10:Mass_dateJuly_3`), type = "10", date = "July_3", iter = 1:nrow(post_fit_11)) 

# 10 trt on July_17
fit_10_J17 <- data.frame(value = exp(post_fit_11$b_Intercept + post_fit_11$b_Treatment10 + post_fit_11$b_Mass_dateJuly_17 + post_fit_11$`b_Treatment10:Mass_dateJuly_17`), type = "10", date = "July_17", iter = 1:nrow(post_fit_11)) 

mu_10 <- rbind(fit_10_J26, fit_10_J10, fit_10_J3, fit_10_J17)
mu_fit <- rbind(mu_0, mu_0.1, mu_1, mu_5, mu_10)
```

# Plot results however you see fit
```{r}
# reorder
mu_fit$date <- factor(mu_fit$date, levels = c("June_26", "July_3", "July_10", "July_17"))

# add color blind palette 
#cbbPalette <- c("#999999", "#E69F00", "#009E73", "#D55E00", "#56B4E9")

# new color palette
colorpalette <- c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b")

M_trt_datep <- mu_fit %>% 
  ggplot(aes(x = type, y = value, fill = type)) +
  geom_violin(position = "dodge") +
  geom_boxplot(outlier.shape = NA, width = 0.1, position = position_dodge(0.9))+
  labs(x = "Treatment (µg/L)", 
       y = "Body Mass (g)",
       caption = "Fig. # Comparison of body mass (g) in Northern Leopard frogs by treatment and date. \nResults are averages and 95% credible intervals from the posterior distribution of a Bayesian \ngeneralized linear mixed model.",
       fill= "Treatment (µg/L)") +
  theme(text= element_text(size=20), 
        plot.title = element_text(face = "bold", hjust = 0.5), 
        plot.caption = element_text(size=10)) +
  theme_classic() + scale_fill_manual(values=colorpalette) + 
  theme(plot.caption = element_text(hjust = 0)) + facet_grid(. ~ date)
M_trt_datep

# save plot
#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/M_trt_datep.tiff", M_trt_datep, dpi=400, width=5, height=3, units="in")
```

# create summary output
```{r}
summary_11 <- mu_fit %>% 
  filter(date == "June_26" | date == "July_17") %>% 
  group_by(type, date) %>% 
  summarize(median = median(value),
            mean = mean(value),
            sd = sd(value),
            low89 = quantile(value, probs = 0.055),
            high89 = quantile(value, probs = 0.945)) %>%
  mutate_if(is.numeric,round,2)
summary_11
```
   type  date    median  mean    sd low89 high89
 1 0     June_26   20.3  20.4  1.44  18.2   22.7
 2 0     July_17   17.9  18.0  1.27  16.1   20.1
 
 3 0.1   June_26   19.0  19.0  1.41  16.8   21.4
 4 0.1   July_17   16.7  16.7  1.24  14.8   18.7
 
 5 1     June_26   17.0  17.1  1.23  15.2   19.1
 6 1     July_17   14.9  14.9  1.07  13.3   16.7
 
 7 5     June_26   19.8  19.8  1.42  17.7   22.2
 8 5     July_17   17.7  17.7  1.27  15.8   19.9
 
 9 10    June_26   15.4  15.4  1.11  13.7   17.2
10 10    July_17   13.2  13.2  0.94  11.7   14.8

# this remakes the graph with means and error bars for Mass on diff dates
```{r}
M_trtp <- summary_11 %>% 
  ggplot(aes(x=type, y=mean, ymin=low89, ymax=high89, fill=date)) + 
  geom_point(size=4, position=position_dodge(width=0.4), shape=21)+
  geom_errorbar(width=0.1, position=position_dodge(width=0.4)) +
  xlab("Treatment (µg/L)")+
  ylab("Body Mass (g)")+
  theme_classic()+
  scale_fill_manual(name="Measurement Date", labels = c("June 26","July 17"),  values = c("grey100","black"))+
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10"))
M_trtp

summary_11 %>% 
  ggplot(aes(x=type, y=mean, ymin=low89, ymax=high89, fill=date)) + 
  geom_point(size=4, position=position_dodge(width=0.4), shape=21)+
  geom_errorbar(width=0.1, position=position_dodge(width=0.4)) +
  xlab("Treatment (µg/L)")+
  ylab("Body Mass (g)")+
  theme_classic()+
  scale_fill_manual(name="Measurement Date", labels = c("June 26","July 17"),  values = c("grey100","black"))+
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10"))

# save plot
#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/M_trtp.tiff", M_trtp, dpi=400, width=5, height=3, units="in")
```

# Compare differences in Mass_dateJune26 and Mass_dateJuly_17 for each trt
```{r}
# trt 0
diff_M0_2617 <- as.data.frame((fit_0_J26$value) - (fit_0_J17$value))
diff_M0_2617 <- diff_M0_2617 %>% 
  rename(mass_loss = '(fit_0_J26$value) - (fit_0_J17$value)')
diff_M0_2617 <- diff_M0_2617 %>% 
  mutate(Treatment = "0")
mean(diff_M0_2617$mass_loss) # 2.381888 (avg body mass loss = 2.4 g)
quantile(diff_M0_2617$mass_loss,probs=c(0.055,0.945)) # (1.736097 , 3.079348)
sum(diff_M0_2617$mass_loss>0)/6000 # >99.99%

# trt 0.1
diff_M0.1_2617 <- as.data.frame((fit_0.1_J26$value) - (fit_0.1_J17$value))
diff_M0.1_2617 <- diff_M0.1_2617 %>% 
  rename(mass_loss = '(fit_0.1_J26$value) - (fit_0.1_J17$value)')
diff_M0.1_2617 <- diff_M0.1_2617 %>% 
  mutate(Treatment = "0.1")
mean(diff_M0.1_2617$mass_loss) # 2.31652
quantile(diff_M0.1_2617$mass_loss,probs=c(0.055,0.945)) # (1.282076 , 3.375572)
sum(diff_M0.1_2617$mass_loss>0)/6000 # 0.9996667

# trt 1
diff_M1_2617 <- as.data.frame((fit_1_J26$value) - (fit_1_J17$value))
diff_M1_2617 <- diff_M1_2617 %>% 
  rename(mass_loss = '(fit_1_J26$value) - (fit_1_J17$value)')
diff_M1_2617 <- diff_M1_2617 %>% 
  mutate(Treatment = "1")
mean(diff_M1_2617$mass_loss) # 2.189514
quantile(diff_M1_2617$mass_loss,probs=c(0.055,0.945)) # (1.631429 2.788458)
sum(diff_M1_2617$mass_loss>0)/6000 # 1

# trt 5
diff_M5_2617 <- as.data.frame((fit_5_J26$value) - (fit_5_J17$value))
diff_M5_2617 <- diff_M5_2617 %>% 
  rename(mass_loss = '(fit_5_J26$value) - (fit_5_J17$value)')
diff_M5_2617 <- diff_M5_2617 %>% 
  mutate(Treatment = "5")
mean(diff_M5_2617$mass_loss) # 2.076317
quantile(diff_M5_2617$mass_loss,probs=c(0.055,0.945)) # (1.432765 2.771573)
sum(diff_M5_2617$mass_loss>0)/6000 # 1

# trt 10
diff_M10_2617 <- as.data.frame((fit_10_J26$value) - (fit_10_J17$value))
diff_M10_2617 <- diff_M10_2617 %>% 
  rename(mass_loss = '(fit_10_J26$value) - (fit_10_J17$value)')
diff_M10_2617 <- diff_M10_2617 %>% 
  mutate(Treatment = "10")
mean(diff_M10_2617$mass_loss) # 2.173212
quantile(diff_M10_2617$mass_loss,probs=c(0.055,0.945)) # (1.645940 2.742987)
sum(diff_M10_2617$mass_loss>0)/6000 # 1
```

# combine all dataframes with mass_loss for each treatment
```{r}
all_mass_loss_2617 <- rbind(diff_M0_2617, diff_M0.1_2617, diff_M1_2617, diff_M5_2617, diff_M10_2617)

all_mass_loss_2617$Treatment <- as.factor(all_mass_loss_2617$Treatment)

all_mass_loss_2617 %>% 
  group_by(Treatment) %>% 
  summarize(mean = mean(mass_loss),
            sd = sd(mass_loss))
```

```{r}
# reorder levels
all_mass_loss_2617$Treatment <- factor(all_mass_loss_2617$Treatment, levels = c("0", "0.1", "1", "5", "10"))

lab <- lab %>% 
  group_by(Animal_ID) %>% 
  mutate(Mass_diff = (Mass_g_June_26) - (Mass_g_July_17))

colorpalette <- c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b")

mass_loss_p <- all_mass_loss_2617 %>% 
  ggplot(aes(x = Treatment, y = mass_loss, fill = Treatment)) +
  geom_violin(position = "dodge") +
  geom_boxplot(outlier.shape = NA, width = 0.1, position = position_dodge(0.9))+
  geom_jitter(data=lab, aes(x=Treatment, y=Mass_diff), shape=21, alpha=0.6) +
  labs(x = "Treatment (µg/L)", 
       y = "Decrease in Body Mass (g)",
       fill= "Treatment (µg/L)") +
  theme(text= element_text(size=20), 
        plot.title = element_text(face = "bold", hjust = 0.5), 
        plot.caption = element_text(size=10)) +
  theme_classic() + scale_fill_manual(values=colorpalette) + 
  theme(axis.text.x = element_text(color="black", size="10")) +
  theme(axis.text.y = element_text(color="black", size="10")) +
  theme(legend.title = element_text(face="bold", size="10"))
mass_loss_p

# save plot
#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/mass_loss_p.tiff", mass_loss_p, dpi=400, width=5, height=3, units="in")
```

# was starting mass different between the control and treatment groups?
```{r}
# 0 vs 0.1 trt
SM_0_0.1 <- fit_0_J26$value - fit_0.1_J26$value
View(SM_0_0.1)
mean(SM_0_0.1)                             # 1.359741
quantile(SM_0_0.1, probs=c(0.055,0.945))   # (-1.752337  4.490054)
sum(SM_0_0.1>0)/6000                       # 0.7545

# 0 vs 1 trt
SM_0_1 <- fit_0_J26$value - fit_1_J26$value
View(SM_0_1)
mean(SM_0_1)                             # 3.295305
quantile(SM_0_1, probs=c(0.055,0.945))   # (0.2741547 6.3458037)
sum(SM_0_1>0)/6000                       # 0.9606667

# 0 vs 5 trt
SM_0_5 <- fit_0_J26$value - fit_5_J26$value
View(SM_0_5)
mean(SM_0_5)                             # 0.5726621
quantile(SM_0_5, probs=c(0.055,0.945))   # (-2.649522  3.817514)
sum(SM_0_5>0)/6000                       # 0.6135%

# 0 vs 10 trt
SM_0_10 <- fit_0_J26$value - fit_10_J26$value
View(SM_0_10)
mean(SM_0_10)                             # 4.997143
quantile(SM_0_10, probs=c(0.055,0.945))   # (2.153778 7.892793)
sum(SM_0_10>0)/6000                       # 0.999%
```

# was final mass different between control and trts?
```{r}
# 0 vs 0.1 trt
FM_0_0.1 <- fit_0_J17$value - fit_0.1_J17$value
mean(FM_0_0.1)                             # 1.294372
quantile(FM_0_0.1, probs=c(0.055,0.945))   # (-1.487836  4.090081)
sum(FM_0_0.1>0)/6000                       # 0.7726667%

# 0 vs 1 trt
FM_0_1 <- fit_0_J17$value - fit_1_J17$value
mean(FM_0_1)                             # 3.102931
quantile(FM_0_1, probs=c(0.055,0.945))   # (0.4199338 5.7475703)
sum(FM_0_1>0)/6000                       # 0.9706667%

# 0 vs 5 trt
FM_0_5 <- fit_0_J17$value - fit_5_J17$value
mean(FM_0_5)                             # 0.2670914
quantile(FM_0_5, probs=c(0.055,0.945))   # (-2.651720  3.096615)
sum(FM_0_5>0)/6000                       # 0.5606667%

# 0 vs 10 trt
FM_0_10 <- fit_0_J17$value - fit_10_J17$value
mean(FM_0_10)                             # 4.788466
quantile(FM_0_10, probs=c(0.055,0.945))   # (2.295294 7.291626)
sum(FM_0_10>0)/6000                       # 0.9991667%
```

# compare Mass gains/loss between trts
```{r}
# 0 vs 0.1 trt
Mdiff0_0.1 <- diff_M0_2617 - diff_M0.1_2617
View(Mdiff0_0.1)
mean(Mdiff0_0.1)                             # 0.06536809
quantile(Mdiff0_0.1, probs=c(0.055,0.945))   # (-0.8183748  0.9424514)
sum(Mdiff0_0.1>0)/6000                       # 0.5488333%

# 0 vs 1 trt
Mdiff0_1 <- diff_M0_2617 - diff_M1_2617
mean(Mdiff0_1)                             # 0.1923736
quantile(Mdiff0_1, probs=c(0.055,0.945))   # (-0.682826 1.097129)
sum(Mdiff0_1>0)/6000                       # 0.6346667%

# 0 vs 5 trt
Mdiff0_5 <- diff_M0_2617 - diff_M5_2617
mean(Mdiff0_5)                             # 0.3055707
quantile(Mdiff0_5, probs=c(0.055,0.945))   # (-0.6546645  1.2718187)
sum(Mdiff0_5>0)/6000                       # 0.6961667%

# 0 vs 10 trt
Mdiff0_10 <- diff_M0_2617 - diff_M10_2617
mean(Mdiff0_10)                             # 0.2086764
quantile(Mdiff0_10, probs=c(0.055,0.945))   # (-0.6548029 1.1005796)
sum(Mdiff0_10>0)/6000                       # 0.6438333%
```