---
title: "Untitled"
author: "Kaitlyn Campbell"
date: "8/16/2021"
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r load libraries}
library(brms)
library(dplyr)
library(ggplot2)
library(tibble)  
library(tidyverse)
library(readr)
library(faintr)
library(devtools)
library(rstan)
library(rstantools)
library(readr)
library(tidybayes)
```
```{r import and wrangle data}
lab <- read_csv("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Brain_IMI_Data.csv")

lab$Treatment <- as.factor(lab$Treatment)

# Rename TL_mm_date columns with just the date
lab <- lab %>% 
  rename(June_26 = TL_mm_June_26) %>% 
  rename(July_17 = TL_mm_July_17)

lab <- lab %>% 
  group_by(Animal_ID) %>% 
  mutate(TL_diff = (July_17) - (June_26))

# Make a new column named 'TL_date' and fill it with the dates that we just created above. Then make another new column named 'TL_mm' and fill the column with TL_mm values that correspond to each date in the new 'TL_date' column
lab_long <- lab %>% 
  gather(key = "TL_date", value = "TL_mm", -Animal_ID, -Treatment, -Mass_g_June_26, -Mass_g_July_3, -Mass_g_July_10, -Mass_g_July_17, -IMI_ng_g_tissue, -IMI_ole_ng_g_tissue, -IMI_ng_mg_protein, -IMI_ole_ng_mg_protein, -CRKT_sec_July_4, -CRKT_sec_July_8, -CRKT_sec_July_11)

# Make Mass_date a factor
lab_long$TL_date <- as.factor(lab_long$TL_date)
lab_long$Treatment <- as.factor(lab_long$Treatment)

```

# gamma distribution
# average adult northern leopard frogs range from 2-4.5 inches (~50 - 115mm)
# exp(4) = 54 mm for average (intercept prior) +/- exp(4) = 54 mm 

```{r load model}
load(file = "/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/saved_models/Models_used_in_paper/mtl5.rda")
```
```{r gamma distribution model}
mtl5 <- brm(TL_mm ~ Treatment * TL_date + (1|Animal_ID), data = lab_long, family = Gamma(link = "log"), 
              prior=c(prior(normal(4, 3), class=Intercept),
                  prior(normal(0, 1), class = b),
                  prior(gamma(0.01,0.01), class="shape")),
          iter = 2000 , warmup = 500, chains = 4, cores = 4,
          seed = 5, save_pars = save_pars(all = TRUE))

print(mtl5, prior=T)
```

```{r model checks}
pp_check(mtl5, type = "dens_overlay", resp = "TL_mm", nsamples=100)
pp_check(mtl5, type = "dens_overlay", resp = "Intercept", nsamples=100)
pp_check(mtl5, type = "dens_overlay", resp = "Treatment", nsamples=100)

lab_long %>%
  tidybayes::add_predicted_draws(model = mtl5, n = 100) %>%
  ungroup() %>%
  ggplot(aes(x = .prediction, group = .draw)) +
  geom_line(stat = 'density',
            alpha = 0.1,
            colour = 'blue') +
  geom_line(stat = 'density',
            data = lab_long,
            mapping = aes(x = TL_mm, group = NULL),
            colour = 'black',
            size = 1.5) +
  scale_y_continuous(NULL, breaks = NULL) +
  labs(x = expression(paste('TL_mm density ')),
       title = 'TL_mm density, actual versus predicted')

loo_mtl5 <- loo(mtl5, save_psis = TRUE, cores = 2, moment_match = TRUE)
print(loo_mtl5) # ok = 41 ; p_loo = 34.8 , se = 3.4
yrep <- posterior_predict(mtl5)
ppc_loo_pit_overlay(lab_long$TL_mm, 
                    yrep = yrep, 
                    lw = weights(loo_mtl5$psis_object))

ppc_intervals(lab_long$TL_mm, yrep = yrep)
ppc_stat(lab_long$TL_mm, yrep = yrep, stat = "mean")
ppc_stat(lab_long$TL_mm, yrep = yrep, stat = "sd")
ppc_stat_grouped(lab_long$TL_mm, group=lab_long$Treatment, yrep = yrep, stat = "mean")
ppc_stat_grouped(lab_long$TL_mm, group=lab_long$Treatment, yrep = yrep, stat = "sd")
```

# Extract posterior
```{r}
set.seed(4545)
post_mtl5 <- posterior_samples(mtl5)    # puts chains of model into data frame
head(post_mtl5)
nrow(post_mtl5) # 6000
```

July_17 = default
```{r compute averages}
# compute averages on for the first day of the experiment (b_Mass_dateJune_26)
as_tibble(post_mtl5) %>% 
  mutate(iteration = 1:nrow(post_mtl5))

Jun26_trt0 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_TL_dateJune_26), type = "0", date = "June 26", iter = 1:nrow(post_mtl5))

Jun26_trt0.1 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_Treatment0.1 + post_mtl5$b_TL_dateJune_26 + post_mtl5$`b_Treatment0.1:TL_dateJune_26`), type = "0.1", date = "June 26", iter = 1:nrow(post_mtl5))

Jun26_trt1 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_Treatment1 + post_mtl5$b_TL_dateJune_26 + post_mtl5$`b_Treatment1:TL_dateJune_26`), type = "1", date = "June 26", iter = 1:nrow(post_mtl5))

Jun26_trt5 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_Treatment5 + post_mtl5$b_TL_dateJune_26 + post_mtl5$`b_Treatment5:TL_dateJune_26`), type = "5", date = "June 26", iter = 1:nrow(post_mtl5))

Jun26_trt10 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_Treatment10 + post_mtl5$b_TL_dateJune_26 + post_mtl5$`b_Treatment10:TL_dateJune_26`), type = "10", date = "June 26", iter = 1:nrow(post_mtl5))

mu_Jun26_trt <- rbind(Jun26_trt0, Jun26_trt0.1, Jun26_trt1, Jun26_trt5, Jun26_trt10)
View(mu_Jun26_trt)

# compute averages on for the last day of the experiment (July 17 - default in model)
Jul17_trt0 <- data.frame(value = exp(post_mtl5$b_Intercept), type = "0", date = "July 17", iter = 1:nrow(post_mtl5))

Jul17_trt0.1 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_Treatment0.1), type = "0.1", date = "July 17", iter = 1:nrow(post_mtl5))

Jul17_trt1 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_Treatment1), type = "1", date = "July 17", iter = 1:nrow(post_mtl5))

Jul17_trt5 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_Treatment5), type = "5", date = "July 17", iter = 1:nrow(post_mtl5))

Jul17_trt10 <- data.frame(value = exp(post_mtl5$b_Intercept + post_mtl5$b_Treatment10), type = "10", date = "July 17", iter = 1:nrow(post_mtl5))

mu_Jul17_trt <- rbind(Jul17_trt0, Jul17_trt0.1, Jul17_trt1, Jul17_trt5, Jul17_trt10)
View(mu_Jul17_trt)

mu_TL <- rbind(mu_Jun26_trt, mu_Jul17_trt)
```

# create summary output
```{r}
summary <- mu_TL %>% 
  group_by(type, date) %>% 
  summarize(mean=mean(value),
            median = median(value),
            sd = sd(value),
            low89 = quantile(value, probs = 0.055),
            high89 = quantile(value, probs = 0.945)) %>%
  mutate_if(is.numeric,round,2)
summary
```

```{r}
summary %>% 
  ggplot(aes(x=type, y=mean, ymin=low89, ymax=high89, fill=date)) + 
  geom_point(size=4, position=position_dodge(width=0.4), shape=21)+
  geom_errorbar(width=0.1, position=position_dodge(width=0.4)) +
  xlab("Treatment (µg/L)")+
  ylab("Total Length (mm)")+
  theme_classic()+
  scale_fill_manual(name="Measurement Date", labels = c("June 26","July 17"),  values = c("grey100","black"))+
  theme(axis.text.x = element_text(color="black", size="10"))+
  theme(axis.text.y = element_text(color="black", size="10"))+
  theme(legend.title = element_text(face="bold", size="10"))
```

# Plot results however you see fit
```{r}
# add color palette 
colorpalette <- c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b")

TL_trt_datep <- mu_TL %>% 
  ggplot(aes(x = type, y = value, fill = type)) +
  geom_violin(position = "dodge") +
  geom_boxplot(outlier.shape = NA, width = 0.1, position = position_dodge(0.9))+
  labs(x = "Treatment (µg/L)", 
       y = "Total body length (mm)",
       caption = "Fig. # Comparison of total body length (mm) in Northern Leopard frogs by treatment and date. \nResults are averages and 95% credible intervals from the posterior distribution of a Bayesian \ngeneralized linear mixed model.",
       fill= "Treatment (µg/L)") +
  theme(text= element_text(size=20), 
        plot.title = element_text(face = "bold", hjust = 0.5), 
        plot.caption = element_text(size=10)) +
  theme_classic() + scale_fill_manual(values=colorpalette) + 
  theme(plot.caption = element_text(hjust = 0)) + facet_grid(.~date)
TL_trt_datep 

# save plot
#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/TL_trt_datep.tiff", TL_trt_datep, dpi=400, width=5, height=3, units="in")
```

# Calculate average growth by trt and determine if final TL was vastly different from starting TL
```{r}
# trt 0
diff_TL0_2617 <- as.data.frame((Jul17_trt0$value) - (Jun26_trt0$value))
diff_TL0_2617 <- diff_TL0_2617 %>% 
  rename(difference = '(Jul17_trt0$value) - (Jun26_trt0$value)')
diff_TL0_2617 <- diff_TL0_2617 %>% 
  mutate(Treatment = "0")

mean(diff_TL0_2617$difference) # 6.617684
quantile(diff_TL0_2617$difference,probs=c(0.055,0.945)) # (3.506098, 9.684612)
sum(diff_TL0_2617$difference>0)/6000 # 0.9998333

# trt 0.1
diff_TL0.1_2617 <- as.data.frame((Jul17_trt0.1$value) - (Jun26_trt0.1$value))
diff_TL0.1_2617 <- diff_TL0.1_2617 %>% 
  rename(difference = '(Jul17_trt0.1$value) - (Jun26_trt0.1$value)')
diff_TL0.1_2617 <- diff_TL0.1_2617 %>% 
  mutate(Treatment = '0.1')

mean(diff_TL0.1_2617$difference) # 12.30424
quantile(diff_TL0.1_2617$difference,probs=c(0.055,0.945)) # (9.343028, 15.349145)
sum(diff_TL0.1_2617$difference>0)/6000 # 1

# trt 1
diff_TL1_2617 <- as.data.frame((Jul17_trt1$value) - (Jun26_trt1$value))
diff_TL1_2617 <- diff_TL1_2617 %>% 
  rename(difference = '(Jul17_trt1$value) - (Jun26_trt1$value)')
diff_TL1_2617 <- diff_TL1_2617 %>% 
  mutate(Treatment = "1")

mean(diff_TL1_2617$difference) # 6.576651
quantile(diff_TL1_2617$difference,probs=c(0.055,0.945)) # (3.571459, 9.556155)
sum(diff_TL1_2617$difference>0)/6000 # 0.9993333

# trt 5
diff_TL5_2617 <- as.data.frame((Jul17_trt5$value) - (Jun26_trt5$value))
diff_TL5_2617 <- diff_TL5_2617 %>% 
  rename(difference = '(Jul17_trt5$value) - (Jun26_trt5$value)')
diff_TL5_2617 <- diff_TL5_2617 %>% 
  mutate(Treatment = "5")

mean(diff_TL5_2617$difference) # 7.418026
quantile(diff_TL5_2617$difference,probs=c(0.055,0.945)) # (4.38806, 10.53762)
sum(diff_TL5_2617$difference>0)/6000 # 0.9991667

# trt 10
diff_TL10_2617 <- as.data.frame((Jul17_trt10$value) - (Jun26_trt10$value))
diff_TL10_2617 <- diff_TL10_2617 %>% 
  rename(difference = '(Jul17_trt10$value) - (Jun26_trt10$value)')
diff_TL10_2617 <- diff_TL10_2617 %>% 
  mutate(Treatment = "10")

mean(diff_TL10_2617$difference) # 5.714901
quantile(diff_TL10_2617$difference,probs=c(0.055,0.945)) # (2.795012, 8.631394)
sum(diff_TL10_2617$difference>0)/6000 # 0.9991667
```

# combine all dataframes with differences for each treatment
```{r}
all_diff_2617 <- rbind(diff_TL0_2617, diff_TL0.1_2617, diff_TL1_2617, diff_TL5_2617, diff_TL10_2617)

all_diff_2617$Treatment <- as.factor(all_diff_2617$Treatment)
```
```{r}
all_diff_2617 %>% 
  group_by(Treatment) %>% 
  summarize(mean = mean(difference),
            sd = sd(difference))
```

# plot
```{r}
# reorder levels
all_diff_2617$Treatment <- factor(all_diff_2617$Treatment, levels = c("0", "0.1", "1", "5", "10"))

colorpalette <- c("#8d96a3","#66a182","#edae49","#6699CC","#d1495b")

TL_trt_diffs <- all_diff_2617 %>% 
  ggplot(aes(x = Treatment, y = difference, fill = Treatment)) +
  geom_violin(position = "dodge") +
  geom_boxplot(outlier.shape = NA, width = 0.1, position = position_dodge(0.9))+
  geom_jitter(data=lab, aes(x=Treatment, y=TL_diff), shape=21, alpha=0.6) +
  labs(x = "Treatment (µg/L)", 
       y = "Increase in Total Body Length (mm)",
       fill= "Treatment (µg/L)") +
  theme(text= element_text(size=20), 
        plot.title = element_text(face = "bold", hjust = 0.5), 
        plot.caption = element_text(size=10)) +
  theme_classic() + scale_fill_manual(values=colorpalette) + 
  theme(axis.text.x = element_text(color="black", size="10")) +
  theme(axis.text.y = element_text(color="black", size="10")) +
  theme(legend.title = element_text(face="bold", size="10"))
TL_trt_diffs

# save plot
#ggsave("/Users/kaitlyn.campbell/OneDrive - The University of South Dakota/Dissertation/Chapter4_Brains_IMI/Lab/Bayes_code/plots/TL_trt_diffs.tiff", TL_trt_diffs, dpi=400, width=5, height=3, units="in")
```

# compare TL gains between trts
```{r}
# 0 vs 0.1 trt
trt_0 <- filter(all_diff_2617, Treatment == 0)
trt_0.1 <- filter(all_diff_2617, Treatment == 0.1)
trt_0_0.1 <- trt_0.1$difference - trt_0$difference
mean(trt_0_0.1) # 5.686559
sd(trt_0_0.1) # 2.686439
quantile(trt_0_0.1, probs=c(0.055,0.945))   # (1.462118 , 9.969254)
sum(trt_0_0.1>0)/6000                       # 0.9821667%

# 0 vs 1 trt
# trt_0 <- filter(all_diff_2617, Treatment == 0)
trt_1 <- filter(all_diff_2617, Treatment == 1)
trt_0_1 <- trt_0$difference - trt_1$difference
mean(trt_0_1) # 0.04103372
quantile(trt_0_1, probs=c(0.055,0.945))   # (-4.233006 , 4.356799)
sum(trt_0_1>0)/6000                       # 0.5113333%

# 0 vs 5 trt
# trt_0 <- filter(all_diff_2617, Treatment == 0)
trt_5 <- filter(all_diff_2617, Treatment == 5)
trt_0_5 <- trt_5$difference - trt_0$difference
mean(trt_0_5) # 0.8003416
quantile(trt_0_5, probs=c(0.055,0.945))   # (-3.571870 , 5.092191)
sum(trt_0_5>0)/6000                       # 0.6206667%

# 0 vs 10 trt
# trt_0 <- filter(all_diff_2617, Treatment == 0)
trt_10 <- filter(all_diff_2617, Treatment == 10)
trt_0_10 <- trt_0$difference - trt_10$difference
mean(trt_0_10) # 0.9027833
quantile(trt_0_10, probs=c(0.055,0.945))   # (-3.361973 , 5.103463)
sum(trt_0_10>0)/6000                       # 0.6376667%


# 0.1 vs 1 trt
# trt_0.1 <- filter(all_diff_2617, Treatment == 0.1)
# trt_1 <- filter(all_diff_2617, Treatment == 1)
trt_0.1_1 <- trt_0.1$difference - trt_1$difference
mean(trt_0.1_1) # 5.727593
quantile(trt_0.1_1, probs=c(0.055,0.945))   # (1.488746 , 9.991618)
sum(trt_0.1_1>0)/6000                       # 0.9851667%

# 0.1 vs 5 trt
# trt_0.1 <- filter(all_diff_2617, Treatment == 0.1)
# trt_5 <- filter(all_diff_2617, Treatment == 5)
trt_0.1_5 <- trt_0.1$difference - trt_5$difference
mean(trt_0.1_5) # 4.886218
quantile(trt_0.1_5, probs=c(0.055,0.945))   # (0.5537514 , 9.2541619)
sum(trt_0.1_5>0)/6000                       # 0.9636667%

# 0.1 vs 10 trt
# trt_0.1 <- filter(all_diff_2617, Treatment == 0.1)
# trt_10 <- filter(all_diff_2617, Treatment == 10)
trt_0.1_10 <- trt_0.1$difference - trt_10$difference
mean(trt_0.1_10) # 6.589343
quantile(trt_0.1_10, probs=c(0.055,0.945))   # (2.385673 , 10.764145)
sum(trt_0.1_10>0)/6000                       # 0.9946667%
```
